Numerical simulation of bubble deformation \\ and breakup under simple linear shear flows

### 2024-04-03 Bubble-deformation.tex
change blue to red, fix caption bug

\usepackage[dvipdfmx]{graphicx}% Include figure files
%\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{comment}
\usepackage{color}
%\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

@@

{\color{blue} Concerning bubble breakup, Wei et

@@

% {\color{blue} What distinguishes our work from that in

@@

In this work we focus on identifying critical flow states numerically, in terms
of dimensionless quantities, that specify the extreme conditions at which a
bubble or drop in shear flow first transitions from deformation to breakup.
We validate our numerical method through comparisons with previous
shear-driven drop dynamics results and we also examine the effect of drop
deformation and breakup sensitivity on domain and grid size.  An advantage of
studying shear-driven bubble deformation and breakup computationally, rather
than experimentally, is that we can easily modify fluid physical properties to
ascertain the sensitivity of deformation and breakup to physical parameters.
In our computations, the time-evolution of the boundary between gas and liquid
is tracked with a coupled level set/volume-of-fluid (CLSVOF) interface
capturing algorithm \cite{SusPuc00,SUSSMAN2007469}.  
We focus on determining critical physical
conditions in which the breakup of a bubble occurs in shear flow because it is
important to identify the parameter regimes in which a relatively simple system
transitions from stable to unstable.  Specifically, we identify the critical
Reynolds number ($Re_{\rm c}$) corresponding to the bubble breakup onset condition as
a function of $Ca$. 
The critical Reynolds number, $Re_{\rm c}$, for drop breakup was 
reported previously by \cite{LiRenRen00}.
{\color{red} In previous studies on the motion of bubble deformation
in a simple shear flow \cite{RusMan02, MulTobDreFisWin08}, only findings for bubble deformation under very low 
$Re$ number conditions ({\color{blue} $Re \ll 1$}) have been reported.}
%{\color{blue} What were the $Re$ conditions considered by \cite{RusMan02, MulTobDreFisWin08} and what are the $Re$ conditions considered in our paper?}
In this work we determine, for the first time, the critical Reynolds number ({\color{blue} $Re \gg 1$}) 
that leads to \emph{bubble} breakup.  Additionally, our computational studies reveal characteristics that
distinguish the deformation and breakup processes of a drop versus those of a bubble.

@@

When comparing with previous drop studies, we fix $\lambda=1$.  As a result,
(for $\lambda=1$) the following dimensionless physical parameters are used to
describe the problem of drop deformation/breakup in shear flow
%
\begin{eqnarray}\label{dimensonless}
  Re = \frac{\rho_{\rm {\color{red}m}}UR}{\mu_{\rm {\color{red}m}}}, \quad
  Ca = \frac{\mu_{\rm {\color{red}m}}U}{\sigma}, \quad
  \eta = \frac{\mu_{\rm b}}{\mu_{\rm m}} 
	\hspace{20pt} m=\mbox{matrix fluid}
\end{eqnarray}
%
$U$ is the velocity scale and $\sigma$ denotes the surface tension.  For the
problem of shear-induced drop deformation and breakup, the velocity is set to
$U = \mathit{\Gamma} R$, where the shear-rate is $\mathit{\Gamma} = 2V/H$.  As
mentioned in the introduction, most previous drop studies set $\eta =
1$ (e.g. \cite{LiRenRen00}).  
Thus, for comparison with previous drop deformation and breakup
problems, we set $\lambda = \eta = 1$ (and also neglect the effect of gravity
so that $g=0$). On the other hand, in our computations for bubble deformation,
we set the density and viscosity of air to be $\rho_{\rm b}$ = 1.2 kg/m$^{3}$
and $\mu_{\rm b} = 1.8 \times 10^{-5}$ Pa$\cdot$s respectively.  We emphasize
that for consistency with previous studies (\cite{LiRenRen00, RusMan02,
MulTobDreFisWin08, KomShaEskDer14, AmaBalCasOli19}), 
%{\color{blue} cite some of these previous studies which examine deformation
%and breakup of a bubble or drop as a function of the $Re$ and $Ca$ numbers.}
we computationally examine the deformation and breakup of a bubble in simple
linear shear flow as a function of the $Re$ and $Ca$ numbers.  {\color{red}
That is to say, by setting $g=0$, we are isolating the effect of only varying
$Re$ and $Ca$ on bubble deformation and breakup.  In our controlled study, we
determine the critical $Re_{\rm c}$ versus $Ca$ curve in which $Re_{\rm c}$
corresponds to the threshold of bubble (or drop) breakup.  We determine the
critical $Re_{\rm c}$ versus $Ca$ curve for strategic pairs of the density
ratio and viscosity ratio. }

@@

%% Ohta
{\color{blue} Next, we examine the validation of our 
computational method in which
we compare with the ``bubble deformation in simple linear shear flow'' 
results reported by
Muller-Fischer et al.~\cite{MulTobDreFisWin08}.  Muller-Fischer et
al.~\cite{MulTobDreFisWin08} experimentally inquired into the bubble
deformation under the condition of $Re \approx 0$. 
In our study, we computed
the bubble deformation on a 
computational domain with dimensions
$\lwh{12}{6}{6}$ and a computational grid in which the finest level grid 
size was
$\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$.
Computations were
performed for the conditions of $Ca = 0.96$ and $Ca = 1.63$ 
with $Re \approx 0$ ($Re = 5.0 \times 10^{-4}$),  
$\lambda = 1.2 \times 10^{-3}$ and  
$\eta \leq 1.2 \times 10^{-6}$.
The parameters that we have prescribed are consistent with the 
experimental conditions by Muller-Fischer et al.
\cite{MulTobDreFisWin08}.  
Comparisons of our numerical results and previous
experimental results (\cite{MulTobDreFisWin08}) are tabulated in
Table~\ref{tab:DeComparisonRe=0}.  
Additionally, in
Table~\ref{tab:DeComparisonRe=0}, we also list experimental results with the
condition of $Re \approx 0$ and $\lambda \approx \eta \approx 0$ by Rust and
Manga (\cite{RusMan02}). These experimental values by Rust and Manga
(\cite{RusMan02}) were obtained from the graph showing the relation of $D$ vs
$Re$ (\cite{RusMan02}).  As is clear from Table~\ref{tab:DeComparisonRe=0}, our
numerical results predicted larger values of $D$ than experimental ones
reported by Muller-Fischer et al.~\cite{MulTobDreFisWin08}. Nevertheless, we
found that our numerical results are very close to the experimental results by
Rust and Manga (\cite{RusMan02}), which emphasizes the intrinsic difficulties
associated with experimental investigations of bubble dynamics, even in simple
linear shear flow.  These comparisons suggest that our computational method is
effective and robust at reproducing bubble dynamics in simple linear shear
flow.}

%%
\begin{table}[tbh]
{\color{blue}
\caption{Comparison of  {\color{red} $D$} for a bubble as a function 
         of $Ca$ ($Re \approx 0$, $\lambda \approx \eta \approx 0$). 
	 In all cases, the domain 
         size is $\lwh{12}{6}{6}$.
         CLSVOF computations used a two-level AMR computational domain 
         with a level-0 discretization $\Delta x^{\ell=0} = \Delta y^{\ell=0} 
         = \Delta z^{\ell=0} = R/8$ and a level-1 discretization
         $\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$.}
 }
\label{tab:DeComparisonRe=0}
%\footnotesize
\center
\begin{tabular}{ c  c  c  c  c }
\hline
\hline
Capillary number & 0.96  & 1.63  \\
{$D$}(Muller-Fischer et al. (\cite{MulTobDreFisWin08}))   & 0.37   &   0.58     \\
{$D$}(Rust and Manga (\cite{RusMan02}))    & $0.71\pm 0.05$   &   $0.81\pm 0.02$     \\
{$D$}(Our study $\Delta x^{\ell=1}=R/16$)  & 0.63   &   0.75     \\
% 8 months compute time.
\hline
\hline
\end{tabular}
\end{table}
%%

@@

%% Ohta
{\color{blue} 
\subsection{Shear stress acting on the bubble}
%  -----------------------------------------------------------------------------
%
%\begin{comment} 
\begin{figure}%[h!]
  \centering
  \includegraphics[width=\textwidth]{ShearStress}
  \caption{Normalized shear stress $\tau^{\ast}$ around a bubble for 
	two Reynolds 
        numbers under the condition of $Ca = 0.3$. The left image shows the 
        shear stress profile at $Re=50$ and the right image at $Re=93$.
   }
  \label{fig:ShearStress}
\end{figure}
%\end{comment} 
%
In the previous section, the appearance of bubble deformation and breakup was
discussed. It is expected that a large deformation and breakup of the bubble
are closely related to the state of shear stress acting on the bubble.
Figure~\ref{fig:ShearStress} shows the shear stress profile around a bubble
for two Reynolds numbers under the condition of $Ca = 0.3$: Reynolds
number equal to 50 and 93.  
The shear stress
profile on the left corresponds to the case of $Re = 50$ and the right side
shows the shear stress profile for the case of $Re = 93$.  
The normalized shear
stress, $\tau^{\ast} = \tau / \tau_{0}$, is defined as a 
ratio of the local shear
stress $\tau = \mu_{\rm m}$$\sqrt{2\bmD:\bmD}$ 
and the apparent shear stress
$\tau_{0} = \mu_{\rm m}$$\mathit{\Gamma}$.  
In this study, for a given $Ca$ condition, the same 
value of $\tau_{0}$ is used regardless of $Re$. 
\par\noindent
For the
case of $Re = 50$, the bubble reaches a deformed stable state.  
\par\noindent
As observed in
previous sections, when the value of $Re$ is slightly below the 
critical $Re$ condition, the bubble does not settle into a deformed 
stable state but instead alternates in an elongation and contraction process.  
In comparison to the $Re=50$ case on the left, the right
image in Fig.~\ref{fig:ShearStress} ($Re=93$)
shows a higher shear stress profile near
the bubble endpoints as it undergoes an elongation
state in the process toward breakup.  
The value of the maximum shear stress for
the case of $Re = 50$ is $\tau ^{\ast} \approx 6$ 
and the maximum shear stress
for the case of $Re = 93$ at the moment 
shown in Fig.~\ref{fig:ShearStress} has
the value of $\tau ^{\ast} \approx 8$.  
The shear stress profile in
Fig.~\ref{fig:ShearStress} (color contour) is drawn in the range from 
$\tau^{\ast} = 1$ to $\tau ^{\ast} = 8$, but, for emphasis, 
shear stress regions
with $\tau ^{\ast} \geqq 6$ are illustrated in red.  
As can be seen in the
figure, the strongest shear stresses are concentrated on the 
ends of the bubble for both $Re$ conditions.  
This indicates that the strong shear stresses acting
on the ends of the bubble are responsible for much of the bubble stretching.
It is important to note that the magnitude of the shear stress acting on the
ends of the bubble for the case of $Re = 93$ is much larger than that for the
case of $Re = 50$.

@@

Table~\ref{tab:CaRecComparison} lists, for representative $Ca$ values, the
corresponding critical Reynolds number, $Re_{\rm c}$, for shear-induced bubble
breakup.  The data in Table~\ref{tab:CaRecComparison} corresponds to $\lambda =
1.2 \times 10^{-3}$, $\eta < 1.0 \times 10^{-3}$, $0.3<Ca<1$, and the
initial/boundary conditions are given by (\ref{IC_BC}).  The results in
Table~\ref{tab:CaRecComparison} indicate that sufficiently large shear forces
are required for bubble breakup even for large Capillary numbers.  In
Figure~\ref{fig:CaRecFit} we plot the smooth interpolant of the data given in
Table~\ref{tab:CaRecComparison} and make the hypothesis that given a new data
point, $(Ca,Re)$,  shear induced bubble break up will occur if the point
$(Ca,Re)$ is above the given critical curve, and the bubble will not break if
the $(Ca,Re)$ pair is below the critical curve.  {\color {red} For comparison,
a critical curve for the drop with $\lambda =\eta = 1$ is also indicated in
Fig.~\ref{fig:CaRecFit}.  The inclusion of breakup and no-breakup critical
curves, for both the drop and the bubble, will facilitate future identification
of $Re_{\rm c}$ numbers---and thus a more complete general critical curve---for
a wide range of high $Ca$ numbers.  }
%{\color{blue} it seems like the above passage is still a work in progress?}
% Yes. I have been suspending computations for bubbles because I have been focussing on non-Newtonian cases, but I have a plan for restarting again.

>>>>

\usepackage[dvipdfmx]{graphicx}% Include figure files
%\usepackage{graphicx}% Include figure files
\usepackage{caption}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{comment}
\usepackage{color}
%\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

@@

{\color{red} Concerning bubble breakup, Wei et

@@

% {\color{red} What distinguishes our work from that in

@@

In this work we focus on identifying critical flow states numerically, in terms
of dimensionless quantities, that specify the extreme conditions at which a
bubble or drop in shear flow first transitions from deformation to breakup.
We validate our numerical method through comparisons with previous
shear-driven drop dynamics results and we also examine the effect of drop
deformation and breakup sensitivity on domain and grid size.  An advantage of
studying shear-driven bubble deformation and breakup computationally, rather
than experimentally, is that we can easily modify fluid physical properties to
ascertain the sensitivity of deformation and breakup to physical parameters.
In our computations, the time-evolution of the boundary between gas and liquid
is tracked with a coupled level set/volume-of-fluid (CLSVOF) interface
capturing algorithm \cite{SusPuc00,SUSSMAN2007469}.  
We focus on determining critical physical
conditions in which the breakup of a bubble occurs in shear flow because it is
important to identify the parameter regimes in which a relatively simple system
transitions from stable to unstable.  Specifically, we identify the critical
Reynolds number ($Re_{\rm c}$) corresponding to the bubble breakup onset condition as
a function of $Ca$. 
The critical Reynolds number, $Re_{\rm c}$, for drop breakup was 
reported previously by \cite{LiRenRen00}.
{\color{red} In previous studies on the motion of bubble deformation
in a simple shear flow \cite{RusMan02, MulTobDreFisWin08}, only findings for bubble deformation under very low 
$Re$ number conditions ({\color{red} $Re \ll 1$}) have been reported.}
%{\color{red} What were the $Re$ conditions considered by \cite{RusMan02, MulTobDreFisWin08} and what are the $Re$ conditions considered in our paper?}
In this work we determine, for the first time, the critical Reynolds 
number ({\color{red} $Re \gg 1$}) 
that leads to \emph{bubble} breakup.  Additionally, our computational studies reveal characteristics that
distinguish the deformation and breakup processes of a drop versus those of a bubble.

@@

When comparing with previous drop studies, we fix $\lambda=1$.  As a result,
(for $\lambda=1$) the following dimensionless physical parameters are used to
describe the problem of drop deformation/breakup in shear flow
%
\begin{eqnarray}\label{dimensonless}
  Re = \frac{\rho_{\rm {\color{red}m}}UR}{\mu_{\rm {\color{red}m}}}, \quad
  Ca = \frac{\mu_{\rm {\color{red}m}}U}{\sigma}, \quad
  \eta = \frac{\mu_{\rm b}}{\mu_{\rm m}} 
	\hspace{20pt} m=\mbox{matrix fluid}
\end{eqnarray}
%
$U$ is the velocity scale and $\sigma$ denotes the surface tension.  For the
problem of shear-induced drop deformation and breakup, the velocity is set to
$U = \mathit{\Gamma} R$, where the shear-rate is $\mathit{\Gamma} = 2V/H$.  As
mentioned in the introduction, most previous drop studies set $\eta =
1$ (e.g. \cite{LiRenRen00}).  
Thus, for comparison with previous drop deformation and breakup
problems, we set $\lambda = \eta = 1$ (and also neglect the effect of gravity
so that $g=0$). On the other hand, in our computations for bubble deformation,
we set the density and viscosity of air to be $\rho_{\rm b}$ = 1.2 kg/m$^{3}$
and $\mu_{\rm b} = 1.8 \times 10^{-5}$ Pa$\cdot$s respectively.  We emphasize
that for consistency with previous studies (\cite{LiRenRen00, RusMan02,
MulTobDreFisWin08, KomShaEskDer14, AmaBalCasOli19}), 
%{\color{red} cite some of these previous studies which examine deformation
%and breakup of a bubble or drop as a function of the $Re$ and $Ca$ numbers.}
we computationally examine the deformation and breakup of a bubble in simple
linear shear flow as a function of the $Re$ and $Ca$ numbers.  {\color{red}
That is to say, by setting $g=0$, we are isolating the effect of only varying
$Re$ and $Ca$ on bubble deformation and breakup.  In our controlled study, we
determine the critical $Re_{\rm c}$ versus $Ca$ curve in which $Re_{\rm c}$
corresponds to the threshold of bubble (or drop) breakup.  We determine the
critical $Re_{\rm c}$ versus $Ca$ curve for strategic pairs of the density
ratio and viscosity ratio. }

@@

%% Ohta
{\color{red} Next, we examine the validation of our 
computational method in which
we compare with the ``bubble deformation in simple linear shear flow'' 
results reported by
Muller-Fischer et al.~\cite{MulTobDreFisWin08}.  Muller-Fischer et
al.~\cite{MulTobDreFisWin08} experimentally inquired into the bubble
deformation under the condition of $Re \approx 0$. 
In our study, we computed
the bubble deformation on a 
computational domain with dimensions
$\lwh{12}{6}{6}$ and a computational grid in which the finest level grid 
size was
$\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$.
Computations were
performed for the conditions of $Ca = 0.96$ and $Ca = 1.63$ 
with $Re \approx 0$ ($Re = 5.0 \times 10^{-4}$),  
$\lambda = 1.2 \times 10^{-3}$ and  
$\eta \leq 1.2 \times 10^{-6}$.
The parameters that we have prescribed are consistent with the 
experimental conditions by Muller-Fischer et al.
\cite{MulTobDreFisWin08}.  
Comparisons of our numerical results and previous
experimental results (\cite{MulTobDreFisWin08}) are tabulated in
Table~\ref{tab:DeComparisonRe=0}.  
Additionally, in
Table~\ref{tab:DeComparisonRe=0}, we also list experimental results with the
condition of $Re \approx 0$ and $\lambda \approx \eta \approx 0$ by Rust and
Manga (\cite{RusMan02}). These experimental values by Rust and Manga
(\cite{RusMan02}) were obtained from the graph showing the relation of $D$ vs
$Re$ (\cite{RusMan02}).  As is clear from Table~\ref{tab:DeComparisonRe=0}, our
numerical results predicted larger values of $D$ than experimental ones
reported by Muller-Fischer et al.~\cite{MulTobDreFisWin08}. Nevertheless, we
found that our numerical results are very close to the experimental results by
Rust and Manga (\cite{RusMan02}), which emphasizes the intrinsic difficulties
associated with experimental investigations of bubble dynamics, even in simple
linear shear flow.  These comparisons suggest that our computational method is
effective and robust at reproducing bubble dynamics in simple linear shear
flow.}

%%
\begin{table}[tbh]
\captionsetup{labelfont={color=red},font={color=red}}

\caption{Comparison of  {\color{red} $D$} for a bubble as a function 
         of $Ca$ ($Re \approx 0$, $\lambda \approx \eta \approx 0$). 
	 In all cases, the domain 
         size is $\lwh{12}{6}{6}$.
         CLSVOF computations used a two-level AMR computational domain 
         with a level-0 discretization $\Delta x^{\ell=0} = \Delta y^{\ell=0} 
         = \Delta z^{\ell=0} = R/8$ and a level-1 discretization
         $\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$.}

\label{tab:DeComparisonRe=0}
%\footnotesize
\center
\begin{tabular}{ c  c  c  c  c }
\hline
\hline
Capillary number & 0.96  & 1.63  \\
{$D$}(Muller-Fischer et al. (\cite{MulTobDreFisWin08}))   & 0.37   &   0.58     \\
{$D$}(Rust and Manga (\cite{RusMan02}))    & $0.71\pm 0.05$   &   $0.81\pm 0.02$     \\
{$D$}(Our study $\Delta x^{\ell=1}=R/16$)  & 0.63   &   0.75     \\
% 8 months compute time.
\hline
\hline
\end{tabular}
\end{table}
%%

@@

%% Ohta
{\color{red} 
\subsection{Shear stress acting on the bubble}
%  -----------------------------------------------------------------------------
%
%\begin{comment} 
\begin{figure}%[h!]
  \centering
  \includegraphics[width=\textwidth]{ShearStress}
  \caption{Normalized shear stress $\tau^{\ast}$ around a bubble for 
	two Reynolds 
        numbers under the condition of $Ca = 0.3$. The left image shows the 
        shear stress profile at $Re=50$ and the right image at $Re=93$.
   }
  \label{fig:ShearStress}
\end{figure}
%\end{comment} 
%
In the previous section, the appearance of bubble deformation and breakup was
discussed. It is expected that a large deformation and breakup of the bubble
are closely related to the state of shear stress acting on the bubble.
Figure~\ref{fig:ShearStress} shows the shear stress profile around a bubble
for two Reynolds numbers under the condition of $Ca = 0.3$: Reynolds
number equal to 50 and 93.  
The shear stress
profile on the left corresponds to the case of $Re = 50$ and the right side
shows the shear stress profile for the case of $Re = 93$.  
The normalized shear
stress, $\tau^{\ast} = \tau / \tau_{0}$, is defined as a 
ratio of the local shear
stress $\tau = \mu_{\rm m}$$\sqrt{2\bmD:\bmD}$ 
and the apparent shear stress
$\tau_{0} = \mu_{\rm m}$$\mathit{\Gamma}$.  
In this study, for a given $Ca$ condition, the same 
value of $\tau_{0}$ is used regardless of $Re$. 
\par\noindent
For the
case of $Re = 50$, the bubble reaches a deformed stable state.  
\par\noindent
As observed in
previous sections, when the value of $Re$ is slightly below the 
critical $Re$ condition, the bubble does not settle into a deformed 
stable state but instead alternates in an elongation and contraction process.  
In comparison to the $Re=50$ case on the left, the right
image in Fig.~\ref{fig:ShearStress} ($Re=93$)
shows a higher shear stress profile near
the bubble endpoints as it undergoes an elongation
state in the process toward breakup.  
The value of the maximum shear stress for
the case of $Re = 50$ is $\tau ^{\ast} \approx 6$ 
and the maximum shear stress
for the case of $Re = 93$ at the moment 
shown in Fig.~\ref{fig:ShearStress} has
the value of $\tau ^{\ast} \approx 8$.  
The shear stress profile in
Fig.~\ref{fig:ShearStress} (color contour) is drawn in the range from 
$\tau^{\ast} = 1$ to $\tau ^{\ast} = 8$, but, for emphasis, 
shear stress regions
with $\tau ^{\ast} \geqq 6$ are illustrated in red.  
As can be seen in the
figure, the strongest shear stresses are concentrated on the 
ends of the bubble for both $Re$ conditions.  
This indicates that the strong shear stresses acting
on the ends of the bubble are responsible for much of the bubble stretching.
It is important to note that the magnitude of the shear stress acting on the
ends of the bubble for the case of $Re = 93$ is much larger than that for the
case of $Re = 50$.

@@

Table~\ref{tab:CaRecComparison} lists, for representative $Ca$ values, the
corresponding critical Reynolds number, $Re_{\rm c}$, for shear-induced bubble
breakup.  The data in Table~\ref{tab:CaRecComparison} corresponds to $\lambda =
1.2 \times 10^{-3}$, $\eta < 1.0 \times 10^{-3}$, $0.3<Ca<1$, and the
initial/boundary conditions are given by (\ref{IC_BC}).  The results in
Table~\ref{tab:CaRecComparison} indicate that sufficiently large shear forces
are required for bubble breakup even for large Capillary numbers.  In
Figure~\ref{fig:CaRecFit} we plot the smooth interpolant of the data given in
Table~\ref{tab:CaRecComparison} and make the hypothesis that given a new data
point, $(Ca,Re)$,  shear induced bubble break up will occur if the point
$(Ca,Re)$ is above the given critical curve, and the bubble will not break if
the $(Ca,Re)$ pair is below the critical curve.  {\color {red} For comparison,
a critical curve for the drop with $\lambda =\eta = 1$ is also indicated in
Fig.~\ref{fig:CaRecFit}.  The inclusion of breakup and no-breakup critical
curves, for both the drop and the bubble, will facilitate future identification
of $Re_{\rm c}$ numbers---and thus a more complete general critical curve---for
a wide range of high $Ca$ numbers.  }
%{\color{red} it seems like the above passage is still a work in progress?}
% Yes. I have been suspending computations for bubbles because I have been focussing on non-Newtonian cases, but I have a plan for restarting again.
